COVID19 - Forecast and predictions using a time dependent SEIR model - Italy

### 2020-03-27 draft_analysis_Italy_new.Rmd
Add home page, navigation and theme

We suppose that the number of total infected $I(t)$ can be the realization of a Poisson random variable
$$
I(t) \sim Poisson (\theta_t)
$$
where $\theta_t$ is the unknown mean of the random process at the time $t$.

The Poisson distribution has a fixed variance that is equal to the mean; in the next part we try to estimates the parameters considering a Negative Binomial distribution which allows for overdispersion.

However, the parameter $\theta_t$ can be supposed to be a realization of a SEIR model with initial parameters $\theta=(\mu,\beta,\sigma, \gamma)$  and initial status $S=(S_{start},E_{start},I_{start},R_{start})$.

The parameter $\sigma$ is our parameter of interest; we estimate $\sigma$ fixing $E_{start}= 3*I_{start}$ minimizing the log likelihood of the described Poisson distribution (or Negative Binomial one).

>>>>

s
